\documentclass[11pt,a4paper]{article}

% ---------- Packages ----------
\usepackage[margin=1.5cm]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}
\usepackage{setspace}

% ---------- Formatting ----------
\setlength{\parindent}{0pt}
\setlength{\parskip}{4pt}

\titleformat{\section}
  {\large\bfseries}{}{0pt}{}[\titlerule]

\titlespacing*{\section}{0pt}{10pt}{6pt}

\newcommand{\cvitem}[2]{\textbf{#1} \hfill #2}

% ---------- Document ----------
\begin{document}

% ---------- Header ----------
\begin{center}
{\LARGE \textbf{Andrew En-maari Yahaya}}\\
\vspace{6pt}

Email: \href{mailto:yahayaenmaariandrew@gmail.com}{yahayaenmaariandrew@gmail.com} \;|\;
LinkedIn: \href{https://www.linkedin.com/in/andrew-en-maari-yahaya-9002b0356}{linkedin.com/in/andrew-en-maari-yahaya} \;|\;
GitHub: \href{https://github.com/Happy-32}{github.com/Happy-32}\;|\;
Phone: +233 547 428 554/ +233 202 262 608 \;|\;
% Portfolio: \href{https://happy-32.github.io/}{happy-32.github.io/}\\
Wa, Ghana
\end{center}

% \vspace{8pt}
\hrule
\vspace{12pt}

% ---------- Education ----------
\section{Education}
\cvitem{BSc Mathematics}{Kwame Nkrumah University of Science and Technology, Ghana}\\
\textit{September 2018 -- November 2022}\\
\begin{itemize}[leftmargin=*, itemsep=2pt]
  \item Relevant coursework: Calculus, Probability and Statistics, Linear Algebra, Numerical Methods, Scientific Computing
  \item Final year project: \textit{House Price Analysis and Prediction using Machine Learning Techniques}
\end{itemize}

% ---------- Skills ----------
\section{Technical Skills}
\textbf{Programming:} Python \\
\textbf{Data Science:} Data cleaning, EDA, Statistical analysis, Machine learning \\
\textbf{Tools:} Pandas, NumPy, Scikit-learn, Matplotlib, Git \\
% \textbf{Databases:} PostgreSQL, MySQL

% ---------- Projects ----------
\section{Projects}
\textbf{Fraud Analysis and Detection} \hfill \textit{2025}\\
\begin{itemize}[leftmargin=*, itemsep=2pt]
  \item Using label/supervised data to predict the probability of fraud occurring based on transaction features.
  \item Methods Used: LightGBM, Random Forest Regression and Logistic Regression.
%   \item Outcomes: Achieved an accuracy of 95\% in detecting fraudulent transactions.
\end{itemize}

\textbf{Student Habit Behavior Analysis} \hfill \textit{2025}\\
\begin{itemize}[leftmargin=*, itemsep=2pt]
  \item Analyzed student behavior patterns using data science techniques.
  \item Methods Used: Data cleaning, EDA, Statistical analysis.
  \item Outcomes: Identified key factors influencing student habits.
\end{itemize}

% ---------- Experience (optional) ----------
\section{Experience}
\begin{itemize}
    \item \textbf{National Service} \hfill Absa Bank Ghana Ltd, Wa Branch December 2022 - October 2023\\
    \begin{itemize}[leftmargin=*, itemsep=2pt]
    \item Assisted customers with account inquiries and transactions.
    \item Managed cash handling and ensured compliance with banking regulations.
    \end{itemize}

    \item \textbf{Lead Generator} \hfill Absa Bank Ghana Ltd, Wa Branch April 2024 - Present\\
    \begin{itemize}[leftmargin=*, itemsep=2pt]
    \item Identifying and reaching out to potential clients for banking products.
    \item Collaborating with the sales team to convert leads into customers.
    \end{itemize}

    \item \textbf{Machine Learning \& AI Trainee} \hfill Thrive Africa, Remote September 2025 - December 2025\\
    \begin{itemize}[leftmargin=*, itemsep=2pt]
    \item Conducted research and analysis on machine learning models.
    \item Collaborated with senior developers to implement ML solutions.
    \end{itemize}

    \item \textbf{AWS Cloud Computing Training} \hfill Thrive Africa, Remote September 2025 - Present\\
    \begin{itemize}[leftmargin=*, itemsep=2pt]
    \item Learning cloud infrastructure and services on AWS platform.
    \item Gaining hands-on experience with cloud deployment and management.
    \end{itemize}
\end{itemize}

% ---------- Certifications / Courses (optional) ----------
\section{Additional Training}
\begin{itemize}[leftmargin=*, itemsep=2pt]
  \item Mastering Web Design: HTML, CSS \& Generative AI -- Udemy (2024)
  \item Data Science \& Machine Learning Training -- Only Quallity Data (2025)
  \item UI/UX Design With Figma -- Udemy (2024)
\end{itemize}

% ---------- Interests ----------
\section{Academic Interests}
\begin{itemize}
    \item Data Science, 
    \item Machine learning, 
    \item Artificial Intelligence, 
    \item Mathematics, 
    \item Cybersecurity,
    \item Programming, 
    \item Web Design, 
    \item Data analysis, 
    \item Applied statistics, 
    \item Real-world data problems, 
\end{itemize}
\end{document}
